Something something

### 2024-08-28 paper/ms.tex
Update fig1 text

>>>>

The main result of our paper is given in Figure~\ref{fig:fig1}. Here, we compare the abundance plane in the Milky Way (left column) to that in our subhalo of interest (middle and right columns). The colored vertical lines show 1D conditional histograms at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at $0.25\,\dex$ higher in the simulations. The \MgFe{} values in the lower panels are given offsets in order to reduce overlap. The rationale for the higher plotted \FeH{} in the simulations comes just from the empirical location of the bimodalities. The Milky Way shows a clear bimodal population, with a high-$\alpha$ sequence most clearly distinct from the low-$\alpha$ sequence at low metallicity. The two sequences merge around solar metallicity.

Our SOI, on the other hand, does not show a clearly bimodal structure in the fiducial simulation (middle column). There is some structure in the $\FeH=-0.75$ bin, but at higher metallicity there is only a weak hint at a second mode in the $\FeH=-0.25$ bin.

The right panel of Figure~\ref{fig:fig1} shows the same distribution as in the middle panel, but with a post-processed declination in \MgFe{}. Star particles formed before $z=1.5$ are given an additive offset of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ and $t_{\textrm{form}}$ is the formation time of the star particle. Only stars formed before $z=1.5$ are shown. A multimodal structure emerges with three clear modes at $\MgFe\sim0.8$, $0.5$, and $0.2\,\dex$. The 1D histograms show that the modes are well-separated, and that the troughs between the modes nearly vanish.
